### 2023-04-19 main.tex
notation

    \begin{equation}\label{InverseS2}
    	\begin{split}
    		\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,\tau_{L}}^{\tau_{1},\ldots,1,\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\right. 
    		\\&+\left. \sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,s_{q_{2}}\ldots,\tau_{L}}^{\tau_{1},\ldots,1,\ldots,1,\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{s_{q_{2}}}\right.
    		\\&+\left.
    		\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{s_{q_{t}},1})\right)e_{\tau_{1},\ldots,s_{q_{L-1}\tau_{L}}}^{1,\ldots,1,\tau_{L}}
    		\right. \\&+ \left. 
    		\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L}}^{1,\ldots,1} \right\}
    	\end{split}
    \end{equation}
    We prove it by induction. When $L=1$ it is true, indeed
    \begin{equation}
    	\mathcal{S}_{2}^{-1}=\sum_{\tau_{1}=1}^{N}\left\{e_{\tau_{1}}^{\tau_{1}}+(1-\delta_{\tau_{1},1})\sum_{q_{1}=1}^{1}\beta_{\tau_{q_{1}}}e_{\tau_{q_{1}}}^{1}\right\}
    \end{equation}
    Assuming that \eqref{InverseS2} is true for arbitrary $L\in \mathbb{N}$, we prove that it holds for $L+1$
\begin{align*}
    	\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}\otimes \mathcal{S}_{2}^{-1}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,\tau_{L}}^{\tau_{1},\ldots,1,\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\right. 
    	\\&+\left. \sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,s_{q_{2}}\ldots,\tau_{L}}^{\tau_{1},\ldots,1,\ldots,1,\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{s_{q_{2}}}\right.
    	\\&+\left.
    	\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{s_{q_{t}},1})\right)e_{\tau_{1},\ldots,s_{q_{L-1}\tau_{L}}}^{1,\ldots,1,\tau_{L}}
    	\right. \\&+ \left. 
    	\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L}}^{1,\ldots,1} \right\}\otimes \sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{L+1}}^{\tau_{L+1}}+(1-\delta_{\tau_{L+1},1})\sum_{q_{1}=1}^{1}\beta_{\tau_{q_{1}}}e_{\tau_{q_{1}}}^{1}\right\}
    	\\&=
    	\sum_{\tau_{1}=1}^{N}\ldots\sum_{s_{L+}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,\tau_{L+1}}+\sum_{q_{1}=1}^{L+1}(1-\delta_{\tau_{q_{1}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,1,\ldots,\tau_{L+1}}\beta_{\tau_{q_{1}}}\right. 
    	\\&+\left. \sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L+1}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,s_{q_{2}}\ldots,\tau_{L+1}}^{\tau_{1},\ldots,1,\ldots,1,\ldots,\tau_{L+1}}\beta_{\tau_{q_{1}}}\beta_{s_{q_{2}}}\right.
    	\\&+\left.
    	\ldots+	\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L}(1-\delta_{s_{q_{t}},1})\right)e_{\tau_{1},\ldots,\tau_{q_{L}}\tau_{L+1}}^{1,\ldots,1,\tau_{L+1}}
    	\right. \\&+ \left. 
    	\left(\prod_{x=1}^{L+1}(1-\delta_{\tau_{x},1})\right)\prod_{x=1}^{L+1}\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L+1}}^{1,\ldots,1} \right\}
    	\\&=
    	\left(\mathcal{S}_{2}^{\otimes L+1}\right)^{-1}
\end{align*}
    \begin{comment}

    \begin{equation}
        S_{2}^{-1}=\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}+Q
    \end{equation}
    where
    \begin{equation}
	Q:=(1-\delta_{\tau_{1},1})\sum_{\tau_{1}=2}^{N}\beta_{\tau_{1}}e_{\tau_{1}}^{1}
\end{equation}
We compute
\begin{equation}
    \begin{split}
        	S_{2}^{-1}\otimes S_{2}^{-1}&=\left(I_{N\times N}+Q\right)\otimes\left(I_{N\times N}+Q\right)
         \\&=
         I_{N\times N}\otimes I_{N\times N}+I_{N\times N}\otimes Q+Q\otimes I_{N\times N}+Q\otimes Q
    \end{split}
\end{equation}
where the addends are 
\begin{equation}
\begin{split}
	&I_{N\times N}\otimes I_{N\times N}=\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}\otimes \sum_{s_{2}=1}^{N}e_{s_{2}}^{s_{2}}=\sum_{\tau_{1},s_{2}=1}^{N}e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}\\
	&I_{N\times N}\otimes Q=(1-\delta_{s_{2},1})\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}\otimes \sum_{s_{2}=2}^{N}\beta_{s_{2}}e_{s_{2}}^{1}=(1-\delta_{s_{2},1})\sum_{\tau_{1}=1,s_{2}=2}^{N}e_{\tau_{1},s_{2}}^{\tau_{1},1}\beta_{s_{2}}\\
	&Q\otimes I_{N\times N}=(1-\delta_{\tau_{1},1})\sum_{\tau_{1}=2}^{N}\beta_{\tau_{1}}e_{\tau_{1}}^{1}\otimes \sum_{s_{2}=1}^{N}e_{s_{2}}^{s_{2}}=(1-\delta_{\tau_{1},1})\sum_{\tau_{1}=2,s_{2}=1}^{N}e_{\tau_{1},s_{2}}^{1,s_{2}}\beta_{\tau_{1}}\\
	&Q\otimes Q=(1-\delta_{\tau_{1},1})(1-\delta_{s_{2},1})\sum_{\tau_{1}=2}^{N}\beta_{\tau_{1}}e_{\tau_{1}}^{1}\otimes \sum_{s_{2}=2}^{N}\beta_{s_{2}}e_{s_{2}}^{1}=(1-\delta_{\tau_{1},1})(1-\delta_{s_{2},1})\sum_{\tau_{1},s_{2}=2}^{N}e_{\tau_{1},s_{2}}^{1,1}\beta_{\tau_{1}}\beta_{s_{2}}
 \end{split}
\end{equation}
The matrix $S_{2}^{-1}\otimes S_{2}^{-1}$ can be written as
\begin{equation}
	\left\{\left(S_{2}^{-1}\otimes S_{2}^{-1}\right)_{\tau_{1},s_{2}}^{q_{1},q_{2}}\right\}_{\tau_{1},s_{2}\in \{1,\ldots,N\}}^{q_{1},q_{2}\in \{1,\ldots,N\}}
\end{equation}
where the subscripts $\tau_{1},s_{2}$ denote the raw and the superscript $q_{1},q_{2}$ the column. Therefore, the raw identified by $\tau_{1},s_{2}$ reads
\begin{equation}
	\left(S_{2}^{-1}\otimes S_{2}^{-1}\right)_{\tau_{1},s_{2}}=e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}+(1-\delta_{s_{2},1})\beta_{s_{2}}e_{\tau_{1},s_{2}}^{\tau_{1},1}+(1-\delta_{\tau_{1},1})\beta_{\tau_{1}}e_{\tau_{1},s_{2}}^{1,s_{2}}+(1-\delta_{\tau_{1},1})(1-\delta_{s_{2},1})\beta_{\tau_{1}}\beta_{s_{2}}e_{\tau_{1},s_{2}}^{1,1}
\end{equation}
\end{comment}
The product $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}|\Psi^{''}\rangle$ gives a vector $|\Psi^{'}\rangle$ whose component are denoted by $\Psi^{'}(\bm{\tau})$. 
To find these elements we need to fix the rows correspondent to $\bm{\tau}$ in the matrix $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}$. Consider a string $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$ with $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, then the corresponding row reads
\begin{equation}
	\begin{split}
\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}_{\bm{\tau}}&=\,e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,\tau_{L}}^{\tau_{1},\ldots,1,\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{s_{q_{2}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,s_{q_{2}}\ldots,\tau_{L}}^{\tau_{1},\ldots,1,\ldots,1,\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{s_{q_{2}}}
  \\&+
  \ldots+\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\prod_{x=1}^{L}\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},1}}e_{\tau_{1},\ldots,\tau_{L}}^{1,\ldots,1}
	\end{split}
\end{equation}

Therefore, we have that 
\begin{equation}\label{ABS_intermediate}
	\begin{split}
		\Psi^{'}(\bm{\tau})&=(\mathcal{S}_{2}^{-1})_{\bm{\tau}}^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},1})\Psi^{''}(\tau_{1},\ldots,\overbrace{1}^{\tau_{q_{1}}},\ldots,\tau_{L})\beta_{q_{1}}\\&+
		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{s_{q_{2}},1})\Psi^{''}(\tau_{1},\ldots,\overbrace{1}^{q_{1}},\ldots,\overbrace{1}^{q_{2}},\ldots,\tau_{L})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(1,\ldots,1)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\prod_{x=1}^{L}\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},1}}
	\end{split}
\end{equation}
For a fixed configuration $\bm{\tau}=(\tau_{1},\ldots,s_{N})$, using equation \eqref{ResulsBasis} and observing that 
\begin{equation}
  \left(1+\sum_{j=y}^{L}\delta_{s_{j},1}\right) =\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{\tau_{y},1})\right)
\end{equation}
we obtain 
    \begin{equation}
\Psi^{''}(\bm{\tau})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},1})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{\tau_{y},1})\right)\right)^{1-\delta_{\tau_{y},1}}
\end{equation}
Introducing
\begin{equation}
	c_{y}=(1-\delta_{\tau_{y},1}) \qquad \forall y\in \{1,\ldots L\}
\end{equation}
and replacing $\Psi^{'}(\bm{\tau})$ computed above in \eqref{ABS_intermediate} we obtain

@@

	\eta_{x}=\begin{cases}
		\tau_{x}\qquad &\text{if}\quad x\neq q_{1},\ldots,q_{b}\\

@@

>>>>

    \begin{equation}\label{InverseS2}
    		\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},1})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}\beta_{\tau_{q_{1}}}\right. 
    		\\&+\left. \sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{\tau_{q_{2}},1})e^{\varphi_{1},\ldots,\varphi_{L}}_{\tau_{1},\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.
    		\\&+\left.
    		\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{\tau_{q_{t}},1})\right)e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}
    		\right. \\&+ \left. 
    		\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}} \right\}
where, $\forall x\in\{1,\ldots,L\}$, we have introduced
	\varphi_{x}(q_{1},\ldots,q_{L})=\begin{cases}
		\tau_{x}\qquad &\text{if}\quad x\notin\{q_{1},\ldots,q_{L}\}\\
		1\qquad &\text{otherwise}\\
The dependence of $\varphi_{x}(q_{1},\ldots,q_{L})$ with respect to $q_{1},\ldots,q_{L}$ is usually understood for the sake of notation.
    We prove it by induction. When $L=1$ it is true, indeed
    	\mathcal{S}_{2}^{-1}=\sum_{\tau_{1}=1}^{N}\left\{e_{\tau_{1}}^{\tau_{1}}+(1-\delta_{\tau_{1},1})\sum_{q_{1}=1}^{1}\beta_{\tau_{q_{1}}}e_{\tau_{q_{1}}}^{1}\right\}
    Assuming that \eqref{InverseS2} is true for arbitrary $L\in \mathbb{N}$, we prove that it holds for $L+1$
    	\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}\otimes \mathcal{S}_{2}^{-1}&=%\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,\tau_{L}}^{\tau_{1},\ldots,1,\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\right. 
    	%\\&+\left. \sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{\tau_{q_{2}},1})e_{\tau_{1},\ldots,\tau_{q_{1}},\ldots,\tau_{q_{2}}\ldots,\tau_{L}}^{\tau_{1},\ldots,1,\ldots,1,\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.
    	%\\&+\left.
    	%\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{s_{q_{t}},1})\right)e_{\tau_{1},\ldots,s_{q_{L-1}\tau_{L}}}^{1,\ldots,1,\tau_{L}}
    	%\right. \\&+ \left. 
    	%\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L}}^{1,\ldots,1} \right\}
    	\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},1})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}\beta_{\tau_{q_{1}}}\right. 
    	\\&+\left. \sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{\tau_{q_{2}},1})e^{\varphi_{1},\ldots,\varphi_{L}}_{\tau_{1},\ldots,\tau_{L}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.
    	\\&+\left.
    	\ldots+	\sum_{q_{1},\ldots,q_{L-1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L-1}(1-\delta_{\tau_{q_{t}},1})\right)e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}
    	\right. \\&+ \left. 
    	\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}} \right\}
    	\otimes \sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{L+1}}^{\tau_{L+1}}+(1-\delta_{\tau_{L+1},1})\sum_{q_{1}=1}^{1}\beta_{\tau_{q_{1}}}e_{\tau_{q_{1}}}^{1}\right\}
    	\sum_{\tau_{1}=1}^{N}\ldots\sum_{s_{L+}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,\tau_{L+1}}+\sum_{q_{1}=1}^{L+1}(1-\delta_{\tau_{q_{1}},1})e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1},\ldots,\varphi_{L+1}}\beta_{\tau_{q_{1}}}\right. 
    	\\&+\left. \sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L+1}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{\tau_{q_{2}},1})e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1},\ldots,\varphi_{L+1}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\right.
    	\\&+\left.
    	\ldots+	\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{t=1}^{L}(1-\delta_{s_{q_{t}},1})\right)e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1},\ldots,\varphi_{L+1}}
    	\right. \\&+ \left. 
    	\sum_{q_{1},\ldots,q_{L+1}=1\,:\,q_{i}\neq q_{j}\,\text{if}\,i\neq j}^{L}\left(\prod_{x=1}^{L+1}(1-\delta_{\tau_{x},1})\right)\beta_{\tau_{x}}e_{\tau_{1},\ldots,\tau_{L+1}}^{\varphi_{1},\ldots,\varphi_{L+1}} \right\}
    	\left(\mathcal{S}_{2}^{\otimes L+1}\right)^{-1}

    \begin{equation}
        S_{2}^{-1}=\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}+Q
    \end{equation}
    where
    \begin{equation}
	Q:=(1-\delta_{\tau_{1},1})\sum_{\tau_{1}=2}^{N}\beta_{\tau_{1}}e_{\tau_{1}}^{1}
\end{equation}
We compute
\begin{equation}
    \begin{split}
        	S_{2}^{-1}\otimes S_{2}^{-1}&=\left(I_{N\times N}+Q\right)\otimes\left(I_{N\times N}+Q\right)
         \\&=
         I_{N\times N}\otimes I_{N\times N}+I_{N\times N}\otimes Q+Q\otimes I_{N\times N}+Q\otimes Q
    \end{split}
\end{equation}
where the addends are 
\begin{equation}
\begin{split}
	&I_{N\times N}\otimes I_{N\times N}=\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}\otimes \sum_{s_{2}=1}^{N}e_{s_{2}}^{s_{2}}=\sum_{\tau_{1},s_{2}=1}^{N}e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}\\
	&I_{N\times N}\otimes Q=(1-\delta_{s_{2},1})\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}\otimes \sum_{s_{2}=2}^{N}\beta_{s_{2}}e_{s_{2}}^{1}=(1-\delta_{s_{2},1})\sum_{\tau_{1}=1,s_{2}=2}^{N}e_{\tau_{1},s_{2}}^{\tau_{1},1}\beta_{s_{2}}\\
	&Q\otimes I_{N\times N}=(1-\delta_{\tau_{1},1})\sum_{\tau_{1}=2}^{N}\beta_{\tau_{1}}e_{\tau_{1}}^{1}\otimes \sum_{s_{2}=1}^{N}e_{s_{2}}^{s_{2}}=(1-\delta_{\tau_{1},1})\sum_{\tau_{1}=2,s_{2}=1}^{N}e_{\tau_{1},s_{2}}^{1,s_{2}}\beta_{\tau_{1}}\\
	&Q\otimes Q=(1-\delta_{\tau_{1},1})(1-\delta_{s_{2},1})\sum_{\tau_{1}=2}^{N}\beta_{\tau_{1}}e_{\tau_{1}}^{1}\otimes \sum_{s_{2}=2}^{N}\beta_{s_{2}}e_{s_{2}}^{1}=(1-\delta_{\tau_{1},1})(1-\delta_{s_{2},1})\sum_{\tau_{1},s_{2}=2}^{N}e_{\tau_{1},s_{2}}^{1,1}\beta_{\tau_{1}}\beta_{s_{2}}
 \end{split}
\end{equation}
The matrix $S_{2}^{-1}\otimes S_{2}^{-1}$ can be written as
\begin{equation}
	\left\{\left(S_{2}^{-1}\otimes S_{2}^{-1}\right)_{\tau_{1},s_{2}}^{q_{1},q_{2}}\right\}_{\tau_{1},s_{2}\in \{1,\ldots,N\}}^{q_{1},q_{2}\in \{1,\ldots,N\}}
\end{equation}
where the subscripts $\tau_{1},s_{2}$ denote the raw and the superscript $q_{1},q_{2}$ the column. Therefore, the raw identified by $\tau_{1},s_{2}$ reads
\begin{equation}
	\left(S_{2}^{-1}\otimes S_{2}^{-1}\right)_{\tau_{1},s_{2}}=e_{\tau_{1},s_{2}}^{\tau_{1},s_{2}}+(1-\delta_{s_{2},1})\beta_{s_{2}}e_{\tau_{1},s_{2}}^{\tau_{1},1}+(1-\delta_{\tau_{1},1})\beta_{\tau_{1}}e_{\tau_{1},s_{2}}^{1,s_{2}}+(1-\delta_{\tau_{1},1})(1-\delta_{s_{2},1})\beta_{\tau_{1}}\beta_{s_{2}}e_{\tau_{1},s_{2}}^{1,1}
\end{equation}
\end{comment}
The product $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}|\Psi^{''}\rangle$ gives a vector $|\Psi^{'}\rangle$ whose component are denoted by $\Psi^{'}(\bm{\tau})$. 
To find these elements we need to fix the rows correspondent to $\bm{\tau}$ in the matrix $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}$. Consider a string $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$ with $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, then the corresponding row reads
\begin{equation}
	\begin{split}
\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}_{\bm{\tau}}&=\,e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},1})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}\beta_{\tau_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{\tau_{q_{2}},1})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}
  \\&+
  \ldots+\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\;\text{if}\;i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},1}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1},\ldots,\varphi_{L}}
	\end{split}
\end{equation}

Therefore, we have that 
\begin{equation}\label{ABS_intermediate}
	\begin{split}
		\Psi^{'}(\bm{\tau})&=(\mathcal{S}_{2}^{-1})_{\bm{\tau}}^{\otimes L}|\Psi^{''}\rangle\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},1})\Psi^{''}(\varphi_{1},\ldots,\varphi_{L})\beta_{q_{1}}\\&+
		\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},1})(1-\delta_{\tau_{q_{2}},1})\Psi^{''}(\varphi_{1},\ldots,\varphi_{L})\beta_{a_{1}}\beta_{a_{2}}\\&+\ldots+\Psi^{''}(1,\ldots,1)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},1})\right)\prod_{x=1}^{L}\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},1}}
	\end{split}
\end{equation}
For a fixed configuration $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$, using equation \eqref{ResulsBasis} and observing that 
\begin{equation}
  \left(1+\sum_{j=y}^{L}\delta_{s_{j},1}\right) =\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{\tau_{y},1})\right)
\end{equation}
we obtain 
    \begin{equation}
\Psi^{''}(\bm{\tau})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},1})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{\tau_{y},1})\right)\right)^{1-\delta_{\tau_{y},1}}
\end{equation}
Introducing
\begin{equation}
	c_{y}=(1-\delta_{\tau_{y},1}) \qquad \forall y\in \{1,\ldots L\}
\end{equation}
and replacing $\Psi^{'}(\bm{\tau})$ computed above in \eqref{ABS_intermediate} we obtain

@@

	\eta_{x}(b)=\begin{cases}
		\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\

@@

The dependence of $\eta_{x}(b)$ with respect to $b$ is usually understood for the sake of notation. 
